Tampering detection for low-power smart cameras

### 2015-05-15 paper.tex
Aggiunto qualcosa...

\author{Adriano Gaibotti\inst{1}\inst{2} \and Claudio Marchisio\inst{1} \and Alexandro Sentinelli\inst{1} \and Giacomo Boracchi\inst{2}}

\institute{ STMicroelectronics, Advanced System Technology, Via Camillo Olivetti 2, 20864, Agrate Brianza (MB), Italy\\
	\email{\{adriano.gaibotti, claudio.marchisio, alexandro.sentinelli\}@st.com}
	\and
	Politecnico di Milano, Dipartimento di Elettronica, Informazione e Bioingegneria (DEIB), Via Ponzio 34/5, 20133, Milano (MI), Italy\\
	\email{adriano.gaibotti@mail.polimi.it, giacomo.boracchi@polimi.it}}
\maketitle

>>>>

\author{Adriano Gaibotti\inst{1}\inst{2} \and Claudio Marchisio\inst{2} \and Alexandro Sentinelli\inst{2} \and Giacomo Boracchi\inst{1}}

\institute{ 
	Politecnico di Milano, Dipartimento di Elettronica, Informazione e Bioingegneria (DEIB), Via Ponzio 34/5, 20133, Milano (MI), Italy\\
	\email{adriano.gaibotti@mail.polimi.it, giacomo.boracchi@polimi.it}
	\and
	STMicroelectronics, Advanced System Technology, Via Camillo Olivetti 2, 20864, Agrate Brianza (MB), Italy\\
	\email{\{adriano.gaibotti, claudio.marchisio, alexandro.sentinelli\}@st.com}
}
\maketitle
